Inference in Hidden Markov Models with Explicit State Duration Distributions

### 2011-11-03 tex/edhmm.tex
crunch crunch crunch (also a couple of typos, updated description of number of transitions graph)
tiny adjustments to the size of the graphical models. I think they're as big as they can get without falling into the gutter
final update

\documentclass[journal]{../inc/oldtran/IEEEtran}
\usepackage{amsmath,amssymb,graphicx,subfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage{algorithm,algorithmic}
\newcommand{\mike}[1]{\textcolor{red}{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}}
\newcommand{\frank}[1]{\textcolor{red}{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}}
\newcommand{\simeon}[1]{\textcolor{red}{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}}
\newcommand{\E}{\textrm{E}}

\title{Inference in Hidden Markov Models with Explicit State Duration Distributions}
\author{Michael Dewar, Chris Wiggins, Frank Wood}

@@

@@

    \begin{figure}[t]
        \centering
        \subfloat[][]{
            \includegraphics[width=0.25\textwidth]{../pic/EDHMM_graphical_model.pdf}
            \label{fig:graphical model}
        }
        \subfloat[][]{
            \includegraphics[width=0.25\textwidth]{../pic/EDHMM_aux_graphical_model.pdf}
         \label{fig:aux graphical model}
        }
        \caption{a) The Explicit Duration Hidden Markov Model. The time left in the current state $x_t$ is denoted $d_t$. The observation at each point in time is denoted $y_t$. b) The EDHMM with the additional auxiliary variable $u_t$ used in the beam sampler.}
    \label{fig:graphs}    
    \end{figure}
\section{Explicit Duration Hidden Markov Model}
\label{sec:Model}

>>>>

\documentclass[journal]{../inc/oldtran/IEEEtran}
\usepackage{amsmath,amssymb,graphicx,subfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage{algorithm,algorithmic}
\newcommand{\E}{\textrm{E}}

@@

\title{Inference in Hidden Markov Models with Explicit State Duration Distributions}
\author{Michael Dewar, Chris Wiggins, Frank Wood}%

%\thanks{Michael Dewar is with bitly, New York City}%
%\thanks{Chris Wiggins is with the Department of Applied Physics and Applied Mathematics, Columbia University}%
%\thanks{Frank Wood is the the Department of Statistics, Columbia Univeristy}%

@@

    \begin{figure}[t]
        \centering
        \subfloat[][]{
            \includegraphics[width=0.23\textwidth]{../pic/EDHMM_graphical_model.pdf}
            \label{fig:graphical model}
        }
        \subfloat[][]{
            \includegraphics[width=0.23\textwidth]{../pic/EDHMM_aux_graphical_model.pdf}
         \label{fig:aux graphical model}
        }
        \caption{a) The Explicit Duration Hidden Markov Model. The time left in the current state $x_t$ is denoted $d_t$. The observation at each point in time is denoted $y_t$. b) The EDHMM with the additional auxiliary variable $u_t$ used in the beam sampler.}
    \label{fig:graphs}    
    \end{figure}
\section{Explicit Duration Hidden Markov Model}
\label{sec:Model}
